---
title: "Basic iCLIP metagenes, inc introns"
output: 
  html_document:
    code_folding: hide
---

We agreed that the most useful representation of the metagenes would be to have a metagene with just the exons, and then have the introns in the corner in a seperate cut out. Thus I have crunched the numbers for introns and exons seperately and will now produce the plots.

```{r}
library(RSQLite)
library(ggplot2)
library(dplyr)
library(tidyr)
db=dbConnect(SQLite(), "../csvdb")
profiles = dbGetQuery(db, "SELECT * FROM basic_iclip_metagenes")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
factor_pal = c("Alyref"=cbPalette[7],
               "Chtop"=cbPalette[4],
               "Nxf1"=cbPalette[8],
               "Cntrl"=cbPalette[3],
               "eIF4A3"=cbPalette[2],
               "PTB"=cbPalette[1],
               "UPF3B"=cbPalette[6])
profiles$pulldown[profiles$pulldown == "FlipIn-FLAG"] = "Cntrl-FLAG"
profiles <- separate(profiles, pulldown, c("protein", "tag"))
```

Now we can plot the images. We will do seperate images for the union of replicates and the indvidual reps.

Unions first

```{r, fig.width=4, fig.height=1.5, dpi=300}
filter(profiles, replicate == "union", interval=="exons") %>%
  ggplot() +
  aes(bin, density, col=protein) +
  geom_vline(xintercept=c(100,200), lty=2, alpha=0.5) +
  geom_line(size=0.7) +
  theme_bw(base_size=9) +
  theme(axis.text=element_text(size=9)) +
  scale_x_continuous(labels = c("Upstream", "Exons", "Downstream"), 
                     breaks=c(50,150,250),
                     name=NULL) +
  scale_y_continuous(breaks=NULL, name="Relative tag density") +
  scale_colour_manual(values=factor_pal, name=NULL, guide=FALSE)-> g
ggsave(filename = "imgs/basic_iclip_metagene_exons.pdf", g, width=4, height=1.5, units="in")
print(g)
```
[Download PDF here](imgs/basic_iclip_metagene_exons.pdf)

We plot the introns seperately as they were computed and normalised seperately. 

```{r, fig.width=1, fig.height=0.8, dpi=300}
filter(profiles, replicate == "union", interval=="introns", bin > 0 & bin <998) %>%
  ggplot() +
  aes(bin, density, col=protein) +
  geom_line(size=0.7) +
  theme_bw(base_size=9) +
  theme(axis.text=element_text(size=9)) + 
  scale_x_continuous(labels = c("Introns"), 
                     breaks=c(50),
                     name=NULL) +
  scale_y_continuous(breaks=NULL, name=NULL) +
  scale_color_manual(guide=FALSE, values=factor_pal) ->   g
ggsave(filename="imgs/basic_iclip_metagenes_introns.pdf", g, width=1, height=0.8)
print(g)
```

[Download PDF here](imgs/basic_iclip_metagenes_introns.pdf)
Now to plot the indevidual reps

```{r, fig.width=4, fig.height=3, dpi=300}
filter(profiles, replicate != "union", interval=="exons") %>%
  ggplot() +
  aes(bin, density, col=protein) +
  geom_vline(xintercept=c(100,200), lty=2, alpha=0.5) +
  geom_line(size=0.7) +
  theme_bw(base_size=9) +
  facet_grid(replicate ~ ., scale="free") + 
  scale_x_continuous(labels = c("Upstream", "Exons", "Downstream"), 
                     breaks=c(50,150,250),
                     name=NULL) +
  scale_y_continuous(breaks=NULL, name="Relative tag density") +
  scale_colour_manual(values=factor_pal, name=NULL) +
  theme(strip.background = element_blank()) -> g
ggsave("imgs/basic_iclip_metagenes_reps.pdf", width = 4, height=3, dpi=300)
print(g)
```
[Download PDF here](imgs/basic_iclip_metagenes_reps.pdf)

and the introns

```{r, fig.width=1, fig.height=1.6, dpi=300}
filter(profiles, replicate != "union", interval=="introns", bin > 0 & bin <998) %>%
  ggplot() +
  aes(bin, density, col=protein) +
  geom_line(size=0.7) +
  theme_bw(base_size=9) +
  scale_x_continuous(labels = c("Introns"), 
                     breaks=c(50),
                     name=NULL) +
  scale_y_continuous(breaks=NULL, name=NULL) +
  scale_color_manual(guide=FALSE, values=factor_pal) +
   facet_grid(replicate ~ ., scale="free") + 
  theme(strip.background = element_blank()) ->   g
ggsave(filename="imgs/basic_iclip_metagenes_introns_reps.pdf", g, width=1, height=0.8)
print(g)
```

[Download PDF here](imgs/basic_iclip_metagenes_introns_reps.pdf)

